Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-06-14 paper/paper.tex
acknowledgment section

\section*{\nmu Author's contributions}
    Text for this section \ldots

\section*{\nmu Acknowledgements}
The Flatiron Institute is a division of the Simons Foundation.

>>>>

%\section*{\nmu Author's contributions}
%    Text for this section \ldots

\section*{\nmu Acknowledgement}
This work is partially supported by the European Research Council (ERC) award 320959 (InvariantClass).
This work is partially supported by the National Science Foundation (NSF) award 1633259 (BIRDVOX).
The Flatiron Institute is a division of the Simons Foundation.
We wish to thank Philippe Brandeis, \'{E}tienne Graindorge, St\'{e}phane Mallat, Adrien Mamou-Mani, and Yan Maresz for contributing to the TICEL research project.
We also wish to thank the students of the Paris Conservatory and all anonymous participants to our study.
